### 2009-06-16 paper.tex
post-submission change to abstract

In our tests, incorporation of basepair structure was the most important factor for alignment accuracy;
appropriate use of posterior-decoding was the next most important factor;
and fine details of the model were least important.
Since posterior-decoding heuristics can be substantially faster than exact phylogenetic inference,
this motivates the use of sum-over-pairs (and approximate sum-over-pairs) heuristics where possible,
with transducer composition reserved for exact ML (or MCMC) inference on phylogenies.
We discuss possible ways to make these phylogenetic inferences tractable.

>>>>

In our tests, incorporation of basepair structure was the most important factor for accurate inference of alignment;
appropriate use of posterior-decoding was the next most important factor;
and fine details of the model were least important.
Since posterior-decoding heuristics can be substantially faster than exact phylogenetic inference,
this motivates the use of sum-over-pairs (and approximate sum-over-pairs) heuristics where possible,
with transducer composition reserved for exact ML (or MCMC) inference on phylogenies.
We discuss possible ways to make these phylogenetic inferences tractable.
